Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
commenting out subsec previous work

\subsection{Previous Work}\label{sec:prevwork}
Our work can be seen as an extension of the \textit{Shingles} idea
described by Casey and Slaney \cite{Casey2006,Casey2007,Casey2008}.
The two main differences are the clustering framework and the use of
beats and bars to select the position of the \textit{Shingles}.

Casey and Slaney \cite{Casey2006} use LSH \cite{Datar2004} to perform
fast approximate nearest neighbor search. Their implementation is E$^2$LSH
\cite{E2LSH}. This package can efficiently handle about $50$K or $100$K
vectors of size $200$. Even with a better implementation, the LSH
model still has some scaling problem. A large portion of the data
must be known to decide how many projections to use, and what guarantee
of finding the nearest neighbor it can provides. Also, we could fix the
number of projections and consider as clusters all the elements that
fall into the same bin. However, this does not give us a centroid, a
typical pattern representing that cluster.

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set. This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column).
}}
\label{fig:codes1}
\end{figure}

@@

\subsection{Artist Recognition}

>>>>

% COMMENTING PREVIOUS WORK
\iffalse
\subsection{Previous Work}\label{sec:prevwork}
Our work can be seen as an extension of the \textit{Shingles} idea
described by Casey and Slaney \cite{Casey2006,Casey2007,Casey2008}.
The two main differences are the clustering framework and the use of
beats and bars to select the position of the \textit{Shingles}.

Casey and Slaney \cite{Casey2006} use LSH \cite{Datar2004} to perform
fast approximate nearest neighbor search. Their implementation is E$^2$LSH
\cite{E2LSH}. This package can efficiently handle about $50$K or $100$K
vectors of size $200$. Even with a better implementation, the LSH
model still has some scaling problem. A large portion of the data
must be known to decide how many projections to use, and what guarantee
of finding the nearest neighbor it can provides. Also, we could fix the
number of projections and consider as clusters all the elements that
fall into the same bin. However, this does not give us a centroid, a
typical pattern representing that cluster.
\fi

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{codes1}
\end{center}
\caption{\small{
Most used codes in the codebook in term of frequency of use in the test
set (artist20, see Subsection \ref{ssec:artist}). 
This codebook was of size $200$ and trained on $2$ bars, pattern
size is $12$x$8$. Code in Figure \ref{fig:code} is the $8$th most used
here (second row, third column). Over the patterns, we display the number of
times it was used out of $71832$ total patterns in the dataset.
}}
\label{fig:codes1}
\end{figure}

@@

\subsection{Artist Recognition} \label{ssec:artist}
